Degrees Draft Syllabus

### 2023-04-04 Draft Syllabus.Rmd
syllabus updates

```{r intro_welcome}

@@

* [Why use R](https://www.youtube.com/watch?v=9kYUGMg_14s)
* [Exercises](https://www.w3schools.com/r/exercise.asp?filename=exercise_syntax1)

@@

* [You can read more about the data types that we do not cover here.](https://www.programiz.com/r/data-types)
* [More information about operators](https://www.statmethods.net/management/operators.html)
* [For a deeper dive into creating custom operators](https://adv-r.hadley.nz/functions.html#infix-functions)

@@

>>>>

@@

* [Codecademy](https://www.codecademy.com/login)
* [Why use R](https://www.youtube.com/watch?v=9kYUGMg_14s)
* [Familiarize yourself with R](https://www.w3schools.com/r/default.asp)

@@

* [Codecademy Lesson](https://www.codecademy.com/courses/learn-r/lessons/introduction-to-r/exercises/why-r)
* [You can read more about the data types that we do not cover here.](https://www.programiz.com/r/data-types)
* [More information about operators](https://www.statmethods.net/management/operators.html)
* [For a deeper dive into creating custom operators](https://adv-r.hadley.nz/functions.html#infix-functions)

@@

* [Codecademy Lesson Pt. 1](https://www.codecademy.com/courses/learn-r/lessons/r-data-frames-intro/exercises/introduction)
* [Codecademy Lesson Pt. 2](https://www.codecademy.com/courses/learn-r/lessons/r-data-frames-modifying/exercises/introduction)
* [More about dplyr](https://dplyr.tidyverse.org/)
